### 2013-07-27 5/applications.tex
updated from Ian's changes

In this chapter, some beneficial applications of the proposed models are presented,
  which demonstrate how the models' consistent sense of variance capability can help to break the vicious circle encountered in SAR speckle
filtering .
This chapter also shows how the MSE can then be 
applicable in the additive and homoskedastic domain to evaluate SAR speckle filters, and further extends the concept to also evaluate
 POLSAR speckle filters.

@@

Given an area to be analyzed, 
  the question of whether it is homogeneous or not can be investigated using
the statistical hypothesis test described in chapter \ref{chap:sar}. 
If that is found to be the case, clustering algorithm can then be applied to partition the area into smaller regions. 
Thus an image can be segmented into homogeneous areas by applying the process repeatedly.

@@

In a window of analysis, intensity dataset $X^I=\{x^I_1,...,x^I_n\}$ follows the exponential distribution given in Eqn. \ref{eqn:SAR Intensity PDF}. 
Assuming prior knowledge of it being homogeneous, thus having a single $\sigma$, the objective then is to estimate $\sigma$. 
This section shows how $\sigma$ can be estimated in log-transformed domain.

It has already been proven that the log-transformed dataset $X^l=\log_2 \sigma$ follows a Fisher-Tippet distribution $pdf(x)= \ln 2 \frac{ 2^d }{ e^{2^d} }$, with $d=x-\mu$, and $\mu=2 \log_2 \sigma$. 
Thus the problem of estimating $\sigma$, casting into the log-transformed domain, equals to the problem of estimating $\mu$. 
The PDF given in Eqn. \ref{eqn:conditional_prob} can then be interpreted as
  the conditional probability of observing a single value of $x^l_i$ when the underlying coefficient equals $\mu$: %is estimated, $\sigma$ can also be estimated $\sigma=2^{ \frac{\mu}{2} }$.

@@

Since log-transformed variables are biased, an MLE approach is used to estimate $\mu$. 
The MLE strategy aims to maximize the conditional (likelihood) probability of observing a set of value X found in the area, given the underlying coefficient equals $\mu$: $P(X^l | \mu )$. 
Assuming the values of $x^l_i$ are independent, the statistical product rule indicates that $P(X^l | \mu )=\displaystyle{\prod^n_{i=1}{P(x^l_i | \mu ) }}$, with  $P(x^l_i | \mu)$ as given in Eqn. \ref{eqn:conditional_prob}.   
%$P(x^l_i | \mu ) = \ln 2 \frac{ 2^{x^l_i - \mu} }{ e^{2^{ x^l_i -\mu }} }$. 
Maximize $P(X^e | \mu )$ also maximizes $\ln[P(X^l | \mu )]$, which can be written as:

@@

Thus $\mu$ can be found by:
\begin{equation}
2^\mu 
	= \frac{ \displaystyle{ \sum^n_{i=1}{ 2^{ x^l_i } }} }{n}  
\label{eqn:mle_log_transform}
\caption{eqn:MLE Estimation in the Log-Transformed Domain}  
\end{equation}

This result in the log-transformed domain is consistent with the analysis result in the original domain where $\sigma^2 = \frac{\sum^n_{i=1}{x^e_i}}{n} $, with $x^e_i = 2^{x^l_i}$

@@

Due to the special characteristics of the log-transformed domain, 
an MLE estimator is used in lieu of the standard averaging estimation for cluster centers. 
Consequently the k-MLE algorithm is presented in Listing \ref{lst:k_mle_algo_cluster_centers}.

@@

  for ( j = 1 to size(c) )
    c_new[j] = maximum_likelyhood_of( l[i] with m[i,j]==1 );
  end for

@@

Compared with using the standard k-means algorithm, the following differences are noted:
%When compared with standard k-means the following differences are evident:
\begin{enumerate}
  \item In k-means, data points are grouped into clusters with minimum distance. 
In our specific situation, as the dispersion PDF is non-symmetric around the cluster center, log-transformed data points are assigned to the cluster that gives them highest likelihood probability.
  \item The calculation of new cluster centers is also different. 
In k-means, new cluster centres are estimated as the average of all membered data points. 
Here, due to the bias of the PDF, maximum likelihood estimations are preferred.
  \item All the design decisions are made possible by the knowledge of the statistical PDF in the log-transformed domain.
\end{enumerate}

@@

In the last section the algorithm was designed with the assumption that the number of clusters are known \textit{a priori}. 
In practice, this is not the case. This section will describe how the issue is to be tackled.

The basic idea is to start with an assumption that the whole area is homogeneous.
Then such an assumption is put to test using the hypothesis testing procedure described earlier. 
If the assumption appears to be violated, the area is broken down by introducing a new cluster center. 
The clustering algorithm is again performed and the new clusters are again assumed to be homogeneous, and tested. 
The process iterates until all partitions are confirmed to be homogeneous. 
The pseudo code for such a procedure is given in Listing \ref{lst:k_mle_algo_partition_number}

\lstset{language=Matlab,caption=Homogenous partitions number growing,label=lst:k_mle_algo_partition_number}
\definecolor{darkgray}{rgb}{0.95,0.95,0.95}
\lstset{backgroundcolor=\color{darkgray}}
\begin{lstlisting}[frame=tb]
function centers = partition_into_homogenous_groups(l, threshold)
  c_init = maximum_likelyhood_of(l);
  [further_partition_needed, c_new] = 
          check_homogeneity_status(l, c_init, threshold);

@@

The principle of speckle filtering is to group pixels into homogeneous areas so that the stochastics noise can be removed.
Hence the k-MLE clustering algorithm can be used to form the basis of a speckle filtering technique.
Specifically the clustered areas directly serves as the grouping of pixels into homogeneous areas, and
the cluster centers serves as the estimated backscattering coefficient for the analysis window.

Considering the case where some extreme threshold-values are used as the homogeneous criteria
If threshold-value is set to a very high value (close to 100\%), then a given partition would almost never be broken down.
The kMLE speckle filter effect would then equals to a box-car filter. 
Conversely, if the threshold-value is set to a very low value (close to 0\%), then a given partition would almost always be broken down to a single value.
The kMLE speckle filtering effect then would be virtually negligible.

@@

One way to improve the speckle filtering  performance is to use a larger window size.
Fig. \ref{fig:boxcar_5x5} shows the visual quality performance of k-MLE filtering on $5 \times 5$ window.
As can be seen, the blurring effect in comparison to $3 \times 3$ filters is clearly visible.
To reduce the associated blurring effect, a threshold-value lower than 100\%  would help by providing an adaptive partitioning of the analysis
window (via the k-MLE clustering algorithm).

@@

Another way to improve the raw k-MLE speckle filter is to apply it iteratively.
As can be seen in Fig. \ref{fig:k_mle_diff_threshold}, a normal 3x3 k-MLE filter would not filter as much noise as a 3x3 boxcar filter. 
At the same time, a 5x5 boxcar filter while having better speckle suppression power, would lose out by its blurring effects as can be seen in Fig. \ref{fig:boxcar_5x5}. 
To improve k-MLE filtering power while avoiding the blurring effect, the k-MLE speckle filter can be used iteratively. 
Presented in the figure \ref{fig:k_mle_filtering_power} is the result of a k-MLE filter configured in a 3x3 window with 25\% threshold-value, being applied iteratively for four times. 
From the plot, the $3 \times 3$ iterative k-MLE filter appears to have similar quantitative performance with the $5 \times 5$ boxcar filter,
  while its visual imagery output appears much sharper, qualitatively speaking.

\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[3x3 25\% 4 iteration k-MLE]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/scene2_filtered_LTH_config_01.eps}
		 \label{variance}
	} 
	\hfill
	\subfloat[Homogenous Error in log-domain]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/k_mle_filter_homogenous_performance.eps}
		 %\epsffile{images/scene2_filtered_LTH_ENL.eps} 
		 \label{variance}
	} 
\end{tabular}
\caption{Improving Homogenous error with iterative k-MLE filter}
\label{fig:k_mle_filtering_power}
\end{figure}

@@

A number of point targets were simulated on a homogeneous background clutter. 
In this test, the SNR between the target and background clutter is fixed at 9dB. 
%The original, speckled images are presented in Figure \ref{fig:sar_point_target_test_boxcar_k_mle}.
Subsequently, the kMLE speckle filter is to be benchmarked against the standard boxcar filters as shown in Fig. \ref{fig:sar_point_target_test_boxcar_k_mle}.
%Both qualitative and quantitative comparisons is done between boxcar filters and the proposed iterative k-MLE filter.
Qualitatively speaking, it is clear that the kMLE speckle filter delivers
a resultant image with both sharper edges than the 5x5 boxcar filter and a stronger visual contrast  than the 3x3 boxcar filter.
%a sharper image than the 5x5 boxcar filter, at the same time its result has better contrast than the 3x3 boxcar filter.
Quantitatively, the k-MLE also appears to have the best histogram response among the 3 filters compared.

@@

The k-MLE filters are also applied on a SLC RadarSat 2 image covering the Muada Merbok area of Malaysia. 
Figure \ref{fig:k_mle_on_RADARSAT2_data} shows the patches of original and filtered images of both natural and urban landscape.
It is obvious that the kMLE speckle filter delivers a significantly ``better'' image than the original data.

@@

As mentioned earlier, speckle filters removes the stochastic noise by grouping data into homogeneous areas. 
In the boxcar filter, the filtering process can be described via Eqn. \ref{eqn:boxcar}, 
where 
	$I_i$ is the intensity value of pixel \textit{i} and
	$n$ is the total number of pixel in the surrounding areas.
The implicit assumption for this filter is that ALL pixels in the surrounding area belongs to the same homogeneous area with the estimating central point.
In the k-MLE filter presented in the previous section and in \citep{Le_2010_ACRS}, the surrounding region is partitioned into homogeneous areas and the approximation is based on Eqn. \ref{eqn:kmle},
where 
	$I_i$ is the intensity value of pixel \textit{i} and
	$k$ is the total number of pixels in the partitioned and homogeneous area covering the centre point.

@@

%The f-MLE speckle filter presented
In this section fuzzy logic approach is followed
  where, instead of fixing on a rigid two-member set of logical values (i.e. true and false),
  embraces truth values that range from 1 to 0.
Thus instead of making a YES/NO decision on whether or not a data point is in the same homogeneous region with the estimated central point, a fuzzy probabilistic scale is calculated.
Then the noise-removal impact of the surrounding data point will be scaled with this probability value.
This fuzzy logic approach give rise to the f-MLE speckle filter presented next,
  and its main benefit is that:  we no longer need to worry about the homogeneous / heterogeneous problem.

@@

The base-2 log transformation is defined as:
${L_I}^i = \log_2{(I^i)}$ 
where 
	$I^i$ is the \textit{$i^{th}$} intensity sample in the originally measured domain,
	$L_I^i$ is the value of that sample in the log-transformed domain.
%Distance in log-transformed domain is defined as:
The contrast is then defined as:
$C= L_I^1 - L_I^2$. 
Assuming $I^i$ follows a negative exponential distribution \citep{Goodman_JOptSocAm_76}, 
  then this dis-similarity distance will follow the distribution 
$pdf(C)= \frac{2^C}{(1+2^C)^2} \ln2$,
  which is consistent.
This analysis is confirmed by real-life data validations (see \cite{Le_2010_ACRS}) and visually demonstrated in Fig. \ref{fig:consistent_contrast_log_domain}.

\subsubsection{F-MLE Estimation}

In this fuzzy logic approach, a pixel with intensity value $I_i$ in the surrounding area of the center point $I_0$ has a likelihood of being in the same homogeneous area given as: 
$p_i = pdf(C_i)$, with $C_i=log_2(I_i) - log_2(I_0)$.
The fMLE approximation is then proposed as written in Eqn. \ref{eqn:fmle_incl}.

%We will see how this works in an homogeneous simulated area.
%The figures demonstrate speckle being filtering effects.
In implementing this statistical estimator, there are very noticeable black dots in the filtered output image.
These dots can be explained as the long-tailed nature of the intensity PDF, 
  which manifests itself in the significant existence of very small values in the population.
In this all-inclusive scheme, there is 
	a single $C_0=0$ (at $I_0$) in the middle of other very large $C_{i, (i > 0)}$, which results in
	a single significant $p_0$ (at $I_0$), and other probably insignificant $p_{i, (i>0)}$.
This marginalizes the filtering power of surrounding pixels.
One way to counter this effect is to exclude the centre point $I_0$ from its estimation,
  which results in the exclusive scheme written in Eqn. \ref{eqn:fmle_excl}.

@@

Fig. \ref{fig:compare_filters_distance_histograms:Filtered:incl} and \ref{fig:compare_filters_distance_histograms:Filtered:excl} plot the filtering treatment described above when applied on the inputs depicted in Fig. \ref{fig:compare_filters_histograms:Original}.
They clearly demonstrate that the F-MLE speckle filters preserves the consistent sense of distance.
This can be explained from the consistent histogram of the input log distance PDF.

Unfortunately, the filtering formula given in Eqn. \ref{eqn:fmle_incl} and Eqn. \ref{eqn:fmle_excl}, especially when applied to large image areas, involves large number of random variables.
%This renders the task of giving analytical PDF for the output log-distance impractical.
This renders the task of deriving an analytical PDF expression impractical for the  log-distance output. 
However, large scale computer simulations can be used to provide a usable histogram, from which a PDF can be estimated.
%from large scale simulations. 
%Simulating experiments with $10^6$ samples is carried out and the histogram information is saved.
Specifically, given a distance $d$, its corresponding probability $pdf(d)$ can be simulated by intrapolating from the saved histogram $y\equiv hist(x)$ at the value of $x \equiv d$.

\subsubsection{Recursively Applying The F-MLE Filters}

The preservation of consistent distance property is the enabling factor that allows the recursive application of F-MLE filters.
Additional execution of the filtering process is be expected to further reduce the random noise power / variance even further.
%In a sense, this scheme is similar to statistical asymptotic estimations, with the added advantage of spatial preservation.

@@

\begin{figure}[H]
\centering
	\subfloat[F-MLE (incl): 123]{
		 \epsfxsize=3.5cm
		 \epsfysize=3.5cm
		 \epsffile{images/incl_distance_pdf_by_iterations.123.made.eps} 
		 \label{fig:plot_incl_distance_pdf_by_iterations.123}
	}
	\subfloat[F-MLE (incl): 456]{
		 \epsfxsize=3.5cm
		 \epsfysize=3.5cm
		 \epsffile{images/incl_distance_pdf_by_iterations.345.made.eps} 
		 \label{fig:plot_incl_distance_pdf_by_iterations.345}
	} 
	\subfloat[F-MLE (excl): 123]{
		 \epsfxsize=3.5cm
		 \epsfysize=3.5cm
		 \epsffile{images/excl_distance_pdf_by_iterations.123.made.eps} 
		 \label{fig:plot_excl_distance_pdf_by_iterations.123}
	}
	\subfloat[F-MLE (excl): 456]{          
		 \epsfxsize=3.5cm
		 \epsfysize=3.5cm
		 \epsffile{images/excl_distance_pdf_by_iterations.345.made.eps} 
		 \label{fig:plot_excl_distance_pdf_by_iterations.345}
	}
\caption{Iteratively Improving in Distance Histograms}
\label{fig:plot_incl_distance_pdf_by_iterations}
\end{figure}

\subsection{Evaluating the F-MLE SAR speckle filters}

@@

The performance of the F-MLE filter is evaluated both qualitatively against real
images and quantitatively via simulated experiments. 
Let us start with a qualitative visual evaluation of the speckle filter on real-captured images.

@@

\begin{figure}
\centering  
      \begin{tabular}[h]{c}
	\subfloat[Original]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.natural.incl.iter0.made.eps} 
		 \label{fig:fmle.natural.incl.iter0}
	} \hfill
	\subfloat[Boxcar]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/boxcar.natural.3x3.made.eps} 
		 \label{fig:boxcar.natural}
	}\\
	\subfloat[F-MLE incl, iter 1]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.natural.incl.iter1.made.eps} 
		 \label{fig:fmle.natural.incl.iter1}
	} \hfill
	\subfloat[F-MLE incl, iter 2]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.natural.incl.iter2.made.eps} 
		 \label{fig:fmle.natural.incl.iter2}
	} \\
	\subfloat[F-MLE excl, iter 1]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.natural.excl.iter1.made.eps} 
		 \label{fig:fmle.natural.excl.iter1}
	} \hfill
	\subfloat[F-MLE excl, iter 2]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.natural.excl.iter2.made.eps} 
		 \label{fig:fmle.natural.excl.iter2}
	} 
	\end{tabular}
\caption{Qualitative Evaluation of F-MLE filter on Real Life Scene of Natural Surface}
\label{fig:fmle.real.images}
\end{figure}

>>>>

In this chapter, some beneficial applications of the proposed models are presented,
  which demonstrate how the models' consistent sense of variance capability can help to break the vicious circle encountered in SAR speckle
filtering.
This chapter also shows how the MSE can then be 
applicable in the additive and homoskedastic domain to evaluate SAR speckle filters, and further extends the concept to also evaluate
 POLSAR speckle filters.

@@

Given an area to be analyzed, 
  the question of whether it is homogeneous or not can be investigated using
the statistical hypothesis test described in chapter \ref{chap:sar}. 
If that is found to be the case, a clustering algorithm can then be applied to partition the area into smaller regions. 
Thus an image can be segmented into homogeneous areas by applying the process repeatedly.

@@

In a window of analysis, intensity dataset $X^I=\{x^I_1,...,x^I_n\}$ follows the exponential distribution given in Eqn. \ref{eqn:SAR Intensity PDF}. 
Assuming prior knowledge of it being homogeneous, thus having a single $\sigma$, the objective then is to estimate $\sigma$. 
This section shows how $\sigma$ can be estimated in the log-transformed domain.

It has already been proven that the log-transformed dataset $X^l=\log_2 \sigma$ follows a Fisher-Tippet distribution $pdf(x)= \ln 2 \frac{ 2^d }{ e^{2^d} }$, with $d=x-\mu$, and $\mu=2 \log_2 \sigma$. 
%***IVM: Hai can you clarify the \ln 2 \frac{ 2^d }{ e^{2^d} }, is that a base 2 in there? Maybe some brackets would help....
Thus the problem of estimating $\sigma$, casting into the log-transformed domain, equals to the problem of estimating $\mu$. 
The PDF given in Eqn. \ref{eqn:conditional_prob} can then be interpreted as
  the conditional probability of observing a single value of $x^l_i$ when the underlying coefficient equals $\mu$: %is estimated, $\sigma$ can also be estimated $\sigma=2^{ \frac{\mu}{2} }$.

@@

Since log-transformed variables are biased, an MLE approach is used to estimate $\mu$. 
The MLE strategy aims to maximize the conditional (likelihood) probability of observing a set of values X found in the area, given that the underlying coefficient equals $\mu$: $P(X^l | \mu )$. 
Assuming the values of $x^l_i$ are independent, the statistical product rule indicates that $P(X^l | \mu )=\displaystyle{\prod^n_{i=1}{P(x^l_i | \mu ) }}$, with  $P(x^l_i | \mu)$ as given in Eqn. \ref{eqn:conditional_prob}.   
%$P(x^l_i | \mu ) = \ln 2 \frac{ 2^{x^l_i - \mu} }{ e^{2^{ x^l_i -\mu }} }$. 
Maximizing $P(X^e | \mu )$ also maximizes $\ln[P(X^l | \mu )]$, which can be written as:

@@

Thus $\mu$ can be found by:
\begin{equation}
2^\mu 
	= \frac{1}{n} \displaystyle{ \sum^n_{i=1}{ 2^{ x^l_i } }}  %***IVM: I edited this slightly to make it look 'nicer'. The same with the next eqn too...
\label{eqn:mle_log_transform}
\caption{eqn:MLE Estimation in the Log-Transformed Domain}  
\end{equation}

This result in the log-transformed domain is consistent with the analysis result in the original domain where $\sigma^2 = \frac{1}{n}\sum^n_{i=1}{x^e_i}$, with $x^e_i = 2^{x^l_i}$

@@

Due to the characteristics of the log-transformed domain, 
an MLE estimator is used in lieu of the standard averaging estimation for cluster centers. 
Consequently the k-MLE algorithm is presented in Listing \ref{lst:k_mle_algo_cluster_centers}.

@@

  for ( j = 1 to size(c) )
    c_new[j] = maximum_likelihood_of( l[i] with m[i,j]==1 );
  end for

@@

Compared with using the standard k-means algorithm, the following differences are noted:
%When compared with standard k-means the following differences are evident:
\begin{enumerate}
  \item In k-means, data points are grouped into clusters with minimum distance. 
In our specific situation, as the dispersion PDF is non-symmetric around the cluster centre, log-transformed data points are assigned to the cluster that gives them highest likelihood probability.
  \item The calculation of new cluster centres is also different. 
In k-means, new cluster centres are estimated as the average of all membered data points. 
Here, due to the bias of the PDF, maximum likelihood estimations are preferred.
  \item All the design decisions are made possible by the knowledge of the statistical PDF in the log-transformed domain.
\end{enumerate}

@@

In the last section the algorithm was designed with the assumption that the number of clusters are known \textit{a priori}. 
In practice, this is not the case. This section will describe how the issue can be tackled with real world data.

The basic idea is to start with an assumption that the whole area is homogeneous.
Then such an assumption is put to test using the hypothesis testing procedure described earlier. 
If the assumption appears to be violated, the area is broken down by introducing a new cluster centre. 
The clustering algorithm is again performed and the new clusters are again assumed to be homogeneous, and tested. 
The process iterates until all partitions are confirmed to be homogeneous. 
The pseudo code for such a procedure is given in Listing \ref{lst:k_mle_algo_partition_number}

\lstset{language=Matlab,caption=Homogeneous partitions number growing,label=lst:k_mle_algo_partition_number}
\definecolor{darkgray}{rgb}{0.95,0.95,0.95}
\lstset{backgroundcolor=\color{darkgray}}
\begin{lstlisting}[frame=tb]
function centers = partition_into_homogenous_groups(l, threshold)
  c_init = maximum_likelihood_of(l);
  [further_partition_needed, c_new] = 
          check_homogeneity_status(l, c_init, threshold);

@@

The principle of speckle filtering is to group pixels into homogeneous areas so that the stochastic noise can be removed.
Hence the k-MLE clustering algorithm can be used to form the basis of a speckle filter.
Specifically, the clustered areas directly serve as the grouping of pixels into homogeneous areas, and
the cluster centres serve as the estimated backscattering coefficient for the analysis window.

Considering the case where some extreme threshold-values are used as the homogeneous criteria,
if threshold-value is set to be very high (close to 100\%), then a given partition would almost never be broken down.
The kMLE speckle filter effect would then equals to a box-car filter. 
Conversely, if the threshold-value is set to a very low value (close to 0\%), then a given partition would almost always be broken down to a single value.
The kMLE speckle filtering effect then would be virtually negligible.

@@

One way to improve the speckle filtering  performance is to use a larger window size.
Fig. \ref{fig:boxcar_5x5} shows the visual quality performance of k-MLE filtering on $5\times5$ window.
As can be seen, the blurring effect in comparison to the $3\times3$ filter is clearly visible.
To reduce the associated blurring effect, a threshold-value lower than 100\%  would help by providing an adaptive partitioning of the analysis
window (via the k-MLE clustering algorithm).

@@

Another way to improve the raw k-MLE speckle filter is to apply it iteratively.
As can be seen in Fig. \ref{fig:k_mle_diff_threshold}, a normal $3\times3$ k-MLE filter would not filter as much noise as a $3\times3$ boxcar filter. 
At the same time, a $5\times5$ boxcar filter, while having better speckle suppression power, would lose out by its blurring effects as can be seen in Fig. \ref{fig:boxcar_5x5}. 
To improve k-MLE filtering power while avoiding the blurring effect, the k-MLE speckle filter can be used iteratively. 
Presented in the figure \ref{fig:k_mle_filtering_power} is the result of a k-MLE filter configured in a $3\times3$ window with 25\% threshold-value, being applied iteratively for four times. 
From the plot, the $3\times 3$ iterative k-MLE filter appears to have similar quantitative performance with the $5\times5$ boxcar filter,
  while its visual imagery output appears much sharper, qualitatively speaking.

\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[3x3 25\% 4 iteration k-MLE]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/scene2_filtered_LTH_config_01.eps}
		 \label{variance}
	} 
	\hfill
	\subfloat[Homogeneous Error in log-domain]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/k_mle_filter_homogenous_performance.eps}
		 %\epsffile{images/scene2_filtered_LTH_ENL.eps} 
		 \label{variance}
	} 
\end{tabular}
\caption{Improving Homogeneous error with iterative k-MLE filter}
\label{fig:k_mle_filtering_power}
\end{figure}

@@

A number of point targets were simulated on a homogeneous background clutter. 
In this test, the SNR between the target and background clutter is fixed at 9dB. 
%The original, speckled images are presented in Figure \ref{fig:sar_point_target_test_boxcar_k_mle}.
Subsequently, the kMLE speckle filter is to be benchmarked against the standard boxcar filters as shown in Fig. \ref{fig:sar_point_target_test_boxcar_k_mle}.
%Both qualitative and quantitative comparisons is done between boxcar filters and the proposed iterative k-MLE filter.
Qualitatively speaking, it is clear that the kMLE speckle filter delivers
a resultant image with both sharper edges than the $5\times5$ boxcar filter and a stronger visual contrast  than the $3\times3$ boxcar filter.
%a sharper image than the 5x5 boxcar filter, at the same time its result has better contrast than the 3x3 boxcar filter.
Quantitatively, the k-MLE also appears to have the best histogram response among the 3 filters compared.

@@

The k-MLE filters are also applied on a SLC RadarSat 2 image covering the Muada Merbok area of Malaysia. 
Figure \ref{fig:k_mle_on_RADARSAT2_data} shows the patches of original and filtered images of both natural and urban landscape.
It is obvious that the k-MLE speckle filter delivers a significantly ``better'' image than the original data.

@@

As mentioned earlier, speckle filters remove the stochastic noise by grouping data into homogeneous areas. 
In the boxcar filter, the filtering process can be described via Eqn. \ref{eqn:boxcar}, 
where 
	$I_i$ is the intensity value of pixel \textit{i} and
	$n$ is the total number of pixels in the surrounding areas.
The implicit assumption for this filter is that ALL pixels in the surrounding area belongs to the same homogeneous area with the estimating central point.
In the k-MLE filter presented in the previous section and in \citep{Le_2010_ACRS}, the surrounding region is partitioned into homogeneous areas and the approximation is based on Eqn. \ref{eqn:kmle},
where 
	$I_i$ is the intensity value of pixel \textit{i} and
	$k$ is the total number of pixels in the partitioned and homogeneous area covering the centre point.

@@

%The f-MLE speckle filter presented
In this section, a fuzzy logic approach is followed
  where, instead of fixing on a rigid two-member set of logical values (i.e. true and false),
the system  embraces truth values that range from 1 to 0.
Thus instead of making a YES/NO decision on whether or not a data point is in the same homogeneous region as the estimated central point, a fuzzy probabilistic scale is calculated.
Then the noise-removal impact of the surrounding data points will be scaled with this probability value.
This fuzzy logic approach give rise to the f-MLE speckle filter presented next,
  and its main benefit is that:  we no longer need to worry about the homogeneous / heterogeneous problem.

@@

The base-2 log transformation is defined as:
${L_I}^i = \log_2{(I^i)}$ 
where 
	$I^i$ is the \textit{$i^{th}$} intensity sample in the originally measured domain,
	$L_I^i$ is the value of that sample in the log-transformed domain.
%Distance in log-transformed domain is defined as:
The contrast is then defined as:
$C= L_I^1 - L_I^2$. 
Assuming that $I^i$ follows a negative exponential distribution \citep{Goodman_JOptSocAm_76}, 
  then this dissimilarity distance will follow the distribution 
$pdf(C)= \frac{2^C}{(1+2^C)^2} \ln2$,
  which is consistent.
This analysis is confirmed by real-life data validations (see \cite{Le_2010_ACRS}) and visually demonstrated in Fig. \ref{fig:consistent_contrast_log_domain}.

\subsubsection{f-MLE Estimation}

In this fuzzy logic approach, a pixel with intensity value $I_i$ in the surrounding area of the centre point $I_0$ has a likelihood of being in the same homogeneous area given as: 
$p_i = pdf(C_i)$, with $C_i=log_2(I_i) - log_2(I_0)$.
The f-MLE approximation is then proposed as written in Eqn. \ref{eqn:fmle_incl}.

%We will see how this works in an homogeneous simulated area.
%The figures demonstrate speckle being filtering effects.
In implementing this statistical estimator, there are very noticeable black dots in the filtered output image.
These dots can be explained by the long-tailed nature of the intensity PDF, 
  which manifests itself in the significant existence of very small values in the population.
In this all-inclusive scheme, there is 
	a single $C_0=0$ (at $I_0$) in the middle of other very large $C_{i, (i > 0)}$, which results in
	a single significant $p_0$ (at $I_0$), and other probably insignificant $p_{i, (i>0)}$.
This marginalizes the filtering power of surrounding pixels.
One way to counter this effect is to exclude the centre point $I_0$ from its estimation,
  which results in the exclusive scheme written in Eqn. \ref{eqn:fmle_excl}.

@@

Fig. \ref{fig:compare_filters_distance_histograms:Filtered:incl} and \ref{fig:compare_filters_distance_histograms:Filtered:excl} plot the filtering treatment described above when applied on the inputs depicted in Fig. \ref{fig:compare_filters_histograms:Original}.
They clearly demonstrate that the f-MLE speckle filters preserve the consistent sense of distance.
This can be explained from the consistent histogram of the input log distance PDF.

Unfortunately, the filtering formula given in Eqn. \ref{eqn:fmle_incl} and Eqn. \ref{eqn:fmle_excl}, especially when applied to large image areas, involves a large number of random variables.
%This renders the task of giving analytical PDF for the output log-distance impractical.
This renders the task of deriving an analytical PDF expression impractical for the  log-distance output. 
However, large scale computer simulations can be used to provide a usable histogram, from which a PDF can be estimated.
%from large scale simulations. 
%Simulating experiments with $10^6$ samples is carried out and the histogram information is saved.
Specifically, given a distance $d$, its corresponding probability $pdf(d)$ can be simulated by interpolating from the saved histogram $y\equiv hist(x)$ at the value of $x \equiv d$.%***IVM: Hai, you had made up a word "intrapolating". It should be either "extrapolating" or "interpolating"... so I've replaced it with the latter...

\subsubsection{Recursively Applying The f-MLE Filters}

The preservation of consistent distance property is the enabling factor that allows the recursive application of f-MLE filters.
Additional execution of the filtering process is be expected to further reduce the random noise power / variance even further.
%In a sense, this scheme is similar to statistical asymptotic estimations, with the added advantage of spatial preservation.

@@

\begin{figure}[H]
\centering
	\subfloat[f-MLE (incl): 123]{
		 \epsfxsize=3.5cm
		 \epsfysize=3.5cm
		 \epsffile{images/incl_distance_pdf_by_iterations.123.made.eps} 
		 \label{fig:plot_incl_distance_pdf_by_iterations.123}
	}
	\subfloat[f-MLE (incl): 456]{
		 \epsfxsize=3.5cm
		 \epsfysize=3.5cm
		 \epsffile{images/incl_distance_pdf_by_iterations.345.made.eps} 
		 \label{fig:plot_incl_distance_pdf_by_iterations.345}
	} 
	\subfloat[f-MLE (excl): 123]{
		 \epsfxsize=3.5cm
		 \epsfysize=3.5cm
		 \epsffile{images/excl_distance_pdf_by_iterations.123.made.eps} 
		 \label{fig:plot_excl_distance_pdf_by_iterations.123}
	}
	\subfloat[f-MLE (excl): 456]{          
		 \epsfxsize=3.5cm
		 \epsfysize=3.5cm
		 \epsffile{images/excl_distance_pdf_by_iterations.345.made.eps} 
		 \label{fig:plot_excl_distance_pdf_by_iterations.345}
	}
\caption{Iteratively Improving in Distance Histograms}
\label{fig:plot_incl_distance_pdf_by_iterations}
\end{figure}

\subsection{Evaluating the f-MLE SAR speckle filters}

@@

The performance of the f-MLE filter is evaluated both qualitatively against real
images and quantitatively via simulated experiments. 
Let us start with a qualitative visual evaluation of the speckle filter on real-captured images.

@@

\begin{figure}
\centering  
      \begin{tabular}[h]{c}
	\subfloat[Original]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.natural.incl.iter0.made.eps} 
		 \label{fig:fmle.natural.incl.iter0}
	} \hfill
	\subfloat[Boxcar]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/boxcar.natural.3x3.made.eps} 
		 \label{fig:boxcar.natural}
	}\\
	\subfloat[f-MLE incl, iter 1]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.natural.incl.iter1.made.eps} 
		 \label{fig:fmle.natural.incl.iter1}
	} \hfill
	\subfloat[f-MLE incl, iter 2]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.natural.incl.iter2.made.eps} 
		 \label{fig:fmle.natural.incl.iter2}
	} \\
	\subfloat[f-MLE excl, iter 1]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.natural.excl.iter1.made.eps} 
		 \label{fig:fmle.natural.excl.iter1}
	} \hfill
	\subfloat[f-MLE excl, iter 2]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.natural.excl.iter2.made.eps} 
		 \label{fig:fmle.natural.excl.iter2}
	} 
	\end{tabular}
\caption{Qualitative Evaluation of f-MLE filter on Real Life Scene of Natural Surface}
\label{fig:fmle.real.images}
\end{figure}
